Notes on Design and Implementation of Anglican

### 2015-07-19 paper/paper.tex
formatting

Anglican is intended to co-exist with Clojure and be a part of
the source of a Clojure program. To facilitate this, Anglican
programs, or queries, are wrapped by macros (defined in the
\texttt{anglican.emit} namespace), which call the CPS
transformations and define Clojure objects suitable for passing
as arguments to inference algorithms (\texttt{defquery},
\texttt{query}). In addition to defining entire queries,
Anglican promotes modularization of inference algorithms through
definition of \textit{probabilistic functions} using
\texttt{defm} and \texttt{fm} (Anglican counterparts of Clojure
\texttt{defn} and \texttt{fn}), which are written in Anglican,
may include probabilistic forms \texttt{sample} and
\texttt{observe} (as well \texttt{predict} for the output), and
can be seamlessly called from inside Anglican queries, just like
functions locally defined within the same query.

Operational semantic of Anglican queries is different from that
of Clojure code, therefore queries must be called through
inference algorithms, rather than `directly'.  The
\texttt{anglican.inference} namespace supplies the
\texttt{infer} multimethod, which accepts an Anglican query and
returns a lazy sequence of weighted samples from the
distribution defined by the query.  When inference
is performed on an Anglican query, the query is run by a
particular inference algorithm. Inference algorithms must
provide an implementation for \texttt{infer}, as well as
override some of the methods of the \textit{checkpoint}
multimethod, called to handle \texttt{sample} and
\texttt{observe} in an algorithmic-specific manner, as well
as on termination of a probabilistic program.

>>>>

Anglican is intended to co-exist with Clojure and be a part of
the source of a Clojure program. To facilitate this, Anglican
programs, or queries, are wrapped by macros (defined in the
\texttt{anglican.emit} namespace), which call the CPS
transformations and define Clojure objects suitable for passing
as arguments to inference algorithms (\texttt{defquery},
\texttt{query}). In addition to defining entire queries,
Anglican promotes modularization of inference algorithms through
definition of \textit{probabilistic functions} using
\texttt{defm} and \texttt{fm} (Anglican counterparts of Clojure
\texttt{defn} and \texttt{fn}). Probabilistic functions are
written in Anglican, may include probabilistic forms
\texttt{sample} and \texttt{observe} (as well \texttt{predict}
for the output), and can be seamlessly called from inside
Anglican queries, just like functions locally defined within the
same query.

Operational semantic of Anglican queries is different from that
of Clojure code, therefore queries must be called through
inference algorithms, rather than `directly'.  The
\texttt{anglican.inference} namespace supplies the
\texttt{infer} multimethod, which accepts an Anglican query and
returns a lazy sequence of weighted samples from the
distribution defined by the query.  When inference
is performed on an Anglican query, the query is run by a
particular inference algorithm. Inference algorithms must
provide an implementation for \texttt{infer}, as well as
override some of the methods of the \texttt{checkpoint}
multimethod, called to handle \texttt{sample} and
\texttt{observe} in an algorithmic-specific manner, as well
as on termination of a probabilistic program.
